\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-05 paper.tex
16. Remedy the oversimple PG numbers analysis with agreeing and transitioning.

The most shocking statistic I found came from Dr. Maressa Orzack, founder and coordinator of Computer Addiction Services \cite{CompAddictionServices}, who cites that up to 40\% of World of Warcraft players could be addicted. \cite{FortyPercentAddicted} If everyone in the world played World of Warcraft, a total of over 7 billion people \cite{WorldPopulation}, and Dr. Ozark's prediction is correct, 2.8 billion people would be addicted. Based purely on the numbers that leaves 60\% of the world's population that is not addicted. A utilitarian view in this case would be that World of Warcraft does not create addiction in the majority of the world and therefore does not diminish mental or physical welfare of the public.

\subsubsection{``Public Good'' Being Improved}
World of Warcraft has over 10 million subscribers \cite{WoWPlayerCount} who average 22 hours of play time per week. \cite{PlayerMotivations} A study published in \emph{Cyberpsychology \& Behavior} \cite{ExcessiveUseForSocialAspects} shows that although World of Warcraft players are passionate about their experiences in the game, they do not show signs of addiction.

>>>>

The most shocking statistic I found came from Dr. Maressa Orzack, founder and coordinator of Computer Addiction Services \cite{CompAddictionServices}, who cites that up to 40\% of World of Warcraft players could be addicted. \cite{FortyPercentAddicted} If everyone in the world played World of Warcraft, a total of over 7 billion people \cite{WorldPopulation}, and Dr. Ozark's prediction is correct, 2.8 billion people would be addicted. Based purely on the numbers that leaves 60\% of the world's population that does not have the mental disease. A utilitarian view in this case would be that World of Warcraft does not create mental disease in the majority of the world and therefore does not diminish mental or physical welfare of the public.

\subsubsection{``Public Good'' Being Improved}
Simple statistics and numbers are not enough to convince me that World of Warcraft is doing good by its players. World of Warcraft has over 10 million subscribers \cite{WoWPlayerCount} who average 22 hours of play time per week. \cite{PlayerMotivations} A study published in \emph{Cyberpsychology \& Behavior} \cite{ExcessiveUseForSocialAspects} shows that although World of Warcraft players are passionate about their experiences in the game, they do not show signs of addiction.
